Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-15 RR_manuscript/Draft_RR.tex
Timo edits

Submitting teams consisted of an average of 3.63 individual analysts (SD = 2.8).

Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from 48.5 to 92 with an average of 69.2 (SD = 11.3).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.

@@

45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.

@@

The models included a mean of 2 different predictors (defined as variables or columns in the data table).
This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
Among the predictors included in the models there were information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or speaker gender.

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
5\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
66\% specified random intercepts only, and 29\% specified random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included 2.4 random terms in their models.
Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of 45 different model specifications.

@@

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

@@

We illustrate what this means in actual acoustic measures by means of examples.
For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.

Table XXX reports the minimum and maximum SD values taken from a representative range.
If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between 0.11 and 0.15, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: \(33.4 * 0.11 = 3.8\) ms, \(51.4 * 0.11 = 5.7\) ms; \(33.4 * 0.15 = 5\) ms, \(51.4 * 0.15 = 7.7\) ms.
We can thus calculate 95\% intervals of the estimated between-model variability in milliseconds: 7.4-11.2 ms based on the low CI estimate 0.11, 9.8-15.1 ms based on the high CI estimate 0.15.

@@

(ref:meta\_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
Notably, while the majority of models yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).

>>>>

Submitting teams consisted of an average of 3.63 individual analysts (SD = 2.8).
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from 48.5 to 92 with an average of 69.2 (SD = 11.3).
We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.

@@

45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
For example,

@@

The models included a mean of 2 different predictors (defined as variables or columns in the data table).
This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
5\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
66\% specified random intercepts only, and 29\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included 2.4 random terms in their models.
Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of 45 different model specifications.

@@

On the one hand, the second non-preregistered model reveals that the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

@@

We illustrate what this means in actual acoustic measures by means of examples.
For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
We then selected values of standard deviations for the three outcome measurements extracted either from specific segments or words across the data tables submitted by the teams (i.e.~how variable were their raw measures).

Table XXX reports the minimum and maximum SD values taken from a representative range.
If we look at segments (e.g.~measures of individual vowels), duration measurements (as taken by the teams who used duration) have standard deviations that range between 33.4 and 51.4 ms.
Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between 0.11 and 0.15, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: \(33.4 * 0.11 = 3.8\) ms, \(51.4 * 0.11 = 5.7\) ms; \(33.4 * 0.15 = 5\) ms, \(51.4 * 0.15 = 7.7\) ms.
We can thus calculate 95\% intervals of the estimated between-model variability in milliseconds: 7.4-11.2 ms based on the low CI estimate 0.11, 9.8-15.1 ms based on the high CI estimate 0.15.

@@

(ref:meta\_plot1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
Notably, while the majority of models yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
